\section{Client Side Browser Defenses}
\label{background:related-browser-defs}

There are many techniques to ``harden'' the browser by limiting what \JS pages
are allowed to execute. These defenses can be split into two categories: those
configured by the user, and those configured by the website author.

In the user-configured category, Adblock~\cite{adblockplus} and
NoScript~\cite{noscriptwebsite} are popular browser
extensions that control what \JS is executed in the browser, based on the
\gls{url} the \JS came from.  Adblock's primary
function is to block ads for aesthetic purposes, but it can also prevent
infection by malware being served in those
ads~\cite{forbes-malware,engadget-malware}.  Adblock blocks feature use by
preventing the loading of resources from certain domains.

NoScript decides whether \JS can execute, based on the \gls{url} the code came
from.  By default, NoScript prevents \JS execution from all origins, rendering
a large swath of the web unusable.  In its default configuration, NoScript
allows \JS execution from a built-in set of trusted origins.  This built-in
allow-list has resulted in a proof of concept exploit via purchasing expired,
allowed domains~\cite{noscript_whitelist}.  Beyond these popular tools,
IceShield~\cite{heiderich2011iceshield} dynamically detects suspicious \JS
calls within the browser, and modifies the \gls{dom} to prevent attacks.

The Tor Browser~\cite{dingledine2004tor} disables, or prompts the user before
using a number of, features by default.  Tor Browser disable many \JS features,
most significantly \textit{SharedWorkers}~\cite{webworkersw3c}, and prompts
users before allowing pages to use the Canvas, GamePad API, WebGL, Battery API,
and Sensor standards~\cite{tor-features}.  These particular features are
disabled because they enable techniques which violate the Tor Browser's
security and privacy goals.

Significant work has been done on hardening the browser architectures, to make them
more resilient to malicious applications attempting to exploit implementation
errors.  Much of this work focuses on isolating or adding access control checks
between different parts of the browser, to prevent a vulnerability in one part
of the browser from imperiling the security of the entire system.  Barth,
Weinberger and Song~\cite{barth2009cross} proposed imposing access control checks
on \JS properties and functions, to prevent certain classes of cross origin
\JS attacks.  Barth et al.~\cite{barth2010protecting} proposed isolating
extensions from high risk resources in the browser's trusted base through
an alternate least-privilege based extension architecture, which has been
adopted as the model for browser extensions in all modern browsers.  Grier,
Tang and King~\cite{grier2008secure} proposed further isolating different
parts of the browser architecture into different operating system level
processes, and using a minimal ``browser kernel'' to organize message passing
between the different isolated elements, a model that mirrors micro-kernel
operating system architectures.  Dong et al.~\cite{dong2013quantitative}
though highlighted that such isolation strategies carry with them significant
performance overheads, and proposed a method for evaluating the costs (in
terms of performance) and benefits (in terms of security risk reduction)
of different isolation schemes.

On the site-author side, \gls{csp} allows server operators to limiting what
kinds of \JS functionality, and sources of code, can be executed, through
either \gls{http} headers, or \gls{html} \textit{meta} tags.
\gls{csp} allows web developers to constrain code on their
sites so that potential attack code cannot access functionality deemed
unnecessary or dangerous~\cite{stamm2010reining}.  Conscript is another
client-side implementation which allows a hosting page to specify policies for
any third-party scripts it includes~\cite{meyerovich2010conscript}.  There are
also a number of technologies selected by the website author but enforced on
the client side,  including Google Caja~\cite{google13caja} and
GATEKEEPER~\cite{guarnieri09gatekeeper}.

There are also models for enforcing policies to limit functionality outside
of the web browser.  Mobile applications use a richer permission model,
where permission to use certain features is asked of the user at either install
or run-time~\cite{android-permissions,au2011short}.
