\chapter{Introduction}

The \gls{www} is possibly the worlds largest open system, allowing information
to be transfer, and individuals to interact, with a speed and ease that would
have been unimaginable only a generation ago.  However, the earliest interactions
for the \gls{www} specified only static documents and form submission systems,
with interactivity limited to applets and plugins.

It wasn't until Netscape introduced \JS to the web in 1996 in Netscape 2.0
that the web as a modern application platform began to develop. Since then,
the web has picked up a large, and quickly growing, set of capabilities,
designed to allow web site authors to deliver new and more complex applications
to users.

This feature growth was initially driven by competition between
browser vendors.  Netscape and Microsoft attempted to gain market advantage
by implementing unique functionality, to entice web authors
to target their browsers, and ensure a larger user base for the browser.
More recently, this feature growth is driven primarily by competition between the
web and ``native'' application platforms, or systems provided by operating
systems, that may provide better performance, or additional functionality, then
web sites can provide.  Each of these efforts to expand the functionality
of the browser has been accompanied by a different marketing slogan (e.x.
DHTML, Web 2.0, HTML5, the browser as OS).

The end result is that the web has changed from a system of static document
retrieval, to a platform for delivering applications that are every bit
as sophisticated as applications delivered and deployed through more
conventional means.  Where websites could once be thought of as simple
collections of images, text and styling instructions (with possible
interactive elements at the periphery), websites now have access to a
range of functionality that rivals ``native'' applications.  Websites can
access graphics cards, create peer-to-peer networks, access IO devices
(e.x. the file system, microphone, ambient light sensor, video camera, VR
devices) and perform high resolution timing operations, among countless other
capabilities.  Browser vendors, working with standards bodies like the \gls{w3c},
aggressively add to the list.

This work presents a systematic evaluation of feature growth on the web, and
to understand the costs and benefits that different features bring to web users.
The overarching goal is to improve the privacy and security of web users
by preventing websites from accessing harmful functionality.  This
work attempts to achieve that goal by understanding

restricting websites to the functionality they need to carry

identify low-benefit, or high-cost, functionality in
the browser, and to

The hypotheses
investigated are that benefit and cost is not distributed equally
across all browser features, second, that most websites only require the
subset of highly-beneficial, low-risk features to carry out the functionality that
web users care about,third,




\input{sections/1_introduction/1_contributions}
\input{sections/1_introduction/2_organization}