\section{Common Terms Used in Work}
\label{intro:terms}

This section presents terms will be used throughout this work.  These terms are
presented upfront to ease the reading of the rest of the work.

A browser \textbf{feature} is a piece of functionality, implemented as
\JS function, method or property, implemented in a web browser, by a browser
vendor.  Browser features are intended to be used by websites, through
\JS delivered by the website, to carry out interactivity and functionality
on the website.  Examples of browser features include
\texttt{HTMLCanvasElement.prototype.toBlob}, used to read the contents of
a \texttt{<canvas>} element in a website into a string, and
\texttt{Document.prototype.getElementById}, used to query an element in a
website.

A \textbf{standard} is a set of related features, defined by a standards
organization, describing what features browser vendors should implement, and
how those features should function.  Standards generally define many features,
intended to be used together to accomplish related goals.  For example, the
\textit{SVG}~\cite{svg2011standard} standard defines features used for creating
and modifying \gls{svg} elements, and the \textit{WebGL}~\cite{webgl2015standard} and
\textit{WebGL 2.0}~\cite{webgl22018standard} standards define features
for performing 3d graphics operations in web pages.

The \textbf{\WAPI} refers to the set of all the features in all of the standards
implemented in modern web browsers. While the implemented \WAPI differs slightly
between modern browsers (for reasons such as differing organizational priorities
or different engineering capabilities), those differences tend to be temporary
and minor.
