\section{Contributions}
\label{intro:contributions}

The underlying motivation, and core thesis, of this work, is that the privacy
and security of web users would be improved, with only small effects on usability,
by restricting the functionality web sites have access to.  This thesis is
explored from several angles in this work.  Specifically, this dissertation
makes the following contributions:

\begin{itemize}
    \item A web-scale measurement of how the \WAPI is used on the web today.
          This study was an automated measurement of browser functionality
          used on sites in the Alexa 10k (at time of measurement), with
          a novel method of distinguishing between \WAPI features used
          for core-site-functionality, and \WAPI features used for
          non-user-serving purposes (e.g. advertising and tracking).
    \item A comprehensive measurement of the costs and benefits of the entire
          \WAPI, broken down by standard.  This work models a standard's
          benefit as the number of sites on the web that require the standard
          to carry out the site's core functionality.  The work models
          a standard's cost in three ways: as the number of publicity
          disclosed vulnerabilities relating to the standard, the number
          of lines of code uniquely needed to implement the standard, and
          the number of papers describing attacks that leverage the standard
          in top security conferences and journals.
    \item Findings learned and vulnerabilities discovered when deploying
          tools to restrict \WAPI access on the web.  These include the
          development of a browser extension that allows for imposing
          access controls on \WAPI features in current browsers, useability
          measurements taken during an in-lab evaluation of the tool, and
          broader findings from real-world use of the extension.
    \item The design and evaluation of CDF, a system of developing and deploying
          web applications with functionality similar to most modern websites,
          but providing client-enforced protections and dataflow
          guarantees.
\end{itemize}
