\section{Conclusions}
\label{cost-benefit:conclusions}

This Chapter presented a systematic evaluation of the costs and benefits that
each standard in the \WAPI brings to browser users, in non-trust,
non-authenticated situations.  This evaluation measured the benefit of each
standard as a function of the number of sites in the Alexa 10k that require
the standard to carry out the site's main purpose, judged from the perspective
of the browser user, not the site operator.  The evaluation measured the cost
of each standard in three ways: first as the number of peer-reviewed papers
in top security conferences and journals that use the standard in an attack,
second as the amount of complexity that the standard's implementation adds
to the code base, and third, as the number of vulnerabilities the standard's
implementation is responsible for.

The most significant results of this work, as it relates to this dissertation's
overarching goal of improving privacy and security on the web, are again, two
related insights.  First, there is a significant subset of functionality in
the \WAPI where the cost to users (in terms of security risk) is much higher
than the benefit (in terms of sites that need the functionality to do what
users care about).  This suggests that web privacy and security could be
improved by restricting which sites can access these low-benefit, high-risk
features.

A second related but distinct important insight is that a small number of
standards in the \WAPI provide the majority of the benefit to browser users.
These same standards, with a few exceptions, carry very little security risk
to users.  This suggests that an application system based around just these
safe, core-web features would provide users with most of the benefits of
modern web applications, with significant security improvements.

The next to Chapters follow these insights to build tools and systems that
improve the privacy and security of web users.  Chapter~\ref{current-web}
pursues the first insight by building tools that restrict the parts of the
\WAPI that existing web applications can access.  Chapter~\ref{future-web}
builds on the second insight by exploring new ways of developing and deploying
web applications that restrict websites to core web functionality, and
emphasize privacy and security over developer expressivity and functionality.
