\acknowledgment
I am extremely grateful to Chris Kanich, my advisor, for his guidance,
encouragement, and good humor.  Without that hat-trick, every part of this
work would be weaker, and I'd still be miserably building PHP websites
at Caribou Coffee.  A deep, sincere, mega-thanks Chris :).

I also grateful to the other members of my committee, Stephen Checkoway,
Jakob Eriksson, Damon McCoy and Venkat Venkatakrishnan, for their generous
time and help.

Thank you too, to my other collaborators. Lara Ansari,
Periwinkle Doerfler, Michael K. Reiter, Cynthia Taylor and Laura Watiker,
I'm glad and grateful I got to work forces with you.

Thanks also to the other BITSLab folks.  Even though we didn't research
together, I'm glad I could take in some of your smarts, charm and general
pleasantness though osmosis. Sara Amini, Tomas Gerlich, Mohammad Ghasemisharif,
Yanzi Jin, Mohammad Taha Khan, Timothy Merrifield, ABM Musa and Sepideh
Roghanchi, thanks for making the six-years more pleasant and fun than they
probably should have been.

I also want to say thank you to the folks who have been angels to me outside of
UIC, without whom this wouldn't have gotten done. Khen Chee Leuk for being the
closest thing possible to a nurse (beside the actual nurses) and helping me
after I goofed it and couldn't move my arms for a bit.  Alan Yu for being
sweet, forgiving and keeping my PhD-ego level headed.  And Sam and Molly
Scranton for helping me not be such as sad-sack.

Finally, I am deeply appreciative to the organizations and grants that
supported me when conducting this work, including the IGERT program (NSF
DGE-1069311) and NSF grants CNS-1351058, CNS-1409868, and CNS-1405886.

Oh yea, and my family: Kristen, Julia, and Peter.  I guess they played some
role in all this.
\initials{PES}
