\authorcontributions

\textbf{Chapter 1} provides an introduction to terms and concepts that will
be used throughout the rest of this work.

\textbf{Chapter 2} gives background
information about the current state of web applications, and recent related
research that has been done to improve web privacy and security.

\textbf{Chapter 3} represents significant portions taken from a pre-print
version of a published paper, Snyder, Peter, et al. ``Browser feature
usage on the modern web.'' \textit{Proceedings of the 2016 Internet Measurement
Conference. ACM}, 2016, for which I was the primary investigator and author.
Lara Ansari performed some of statistical analysis and measurement of prior
\FF versions.  Cynthia Taylor contributed to the writing of the paper, along
with the planning and vetting of the direction of the work.  My advisor,
Chris Kanich, also contributed to the writing of the paper, in addition to the
planning and structure of the project.

\textbf{Chapters 4 and 5} present portions of a pre-print version of a
published paper, Snyder, Peter,
Cynthia Taylor, and Chris Kanich. ``Most Websites Don't Need to Vibrate: A
Cost-Benefit Approach to Improving Browser Security.'' \textit{Proceedings of the 2017
ACM SIGSAC Conference on Computer and Communications Security. ACM}, 2017.,
for which I was the primary investigator and author.  Cynthia Taylor contributed
to the writing of the paper, along with the planning and vetting of the
direction of the work.  My advisor, Chris Kanich, also contributed to the
writing of the paper, in addition to the planning and structure of the project.
Subsections \ref{current-web:extension-deployment} and
\ref{current-web:conclusions} describe work preformed solely by the author of
this dissertation.

\textbf{Chapter 6} present portions of a pre-print version of a third
published paper, Snyder, Peter, et al. ``CDF: Predictably Secure Web
Documents.'' \textit{Proceedings of the Workshop on Technology and Consumer
Protection}, 2017, for which I was the primary investigator and author.  Laura Watiker contributed
some of the useability analysis, and Cynthia Taylor and Chris Kanich
contributed writing and guidance in the direction and evaluation of the described
system.

\textbf{Chapter 6} concludes with a discussion of how the previous chapters
jointly contribute to our understanding of web privacy and security
vulnerabilities, along with some suggestions of how these findings could
be built on by further research.