\vita
\begin{singlespace}
    \begin{description}[labelwidth=4cm,leftmargin=4.2cm,itemsep=1em]

        \item[NAME] Peter Edwin Snyder

        \item[EDUCATION] B.A., Political Science, Lawrence University, Appleton, WI, 2006

        \item[TEACHING] Department of Computer Science, University of Illinois at Chicago, Software Design (CS342, Summer 2017)

        \item[PUBLICATIONS]
            \begin{itemize}[label={},listparindent=0pt,itemindent=0pt,leftmargin=0pt,itemsep=1em,parsep=0pt,topsep=0pt,partopsep=0pt]
                \item Peter Snyder, Cynthia Taylor, and Chris Kanich. %
                ``Most Websites Dont Need to Vibrate: A Cost-Benefit Approach to Improving Browser Security.'' %
                In Proceedings of the 2017 ACM Conference on Computer and Communications Security (CCS, 2017).

                \item Peter Snyder, Periwinkle Doerfler, Chris Kanich, and Damon McCoy. %
                ``Fifteen Minutes of Unwanted Fame: Detecting and Characterizing Doxing.'' %
                In Proceedings of the 2017 Internet Measurement Conference (IMC, 2017).

                \item Peter Snyder, Laura Watiker, Cynthia Taylor, and Chris Kanich. %
                ``CDF: Predictably Secure Web Documents.'' %
                In Proceedings of the 2017 IEEE Workshop on Technology and Consumer Protection (ConPro, 2017).

                \item Peter Snyder, Lara Ansari, Cynthia Taylor, and Chris Kanich. %
                ``Browser Feature Usage on The Modern Web.'' %
                In Proceedings of the 2016 ACM Internet Measurement Conference (IMC, 2016).

                \item Peter Snyder and Chris Kanich. %
                ``Characterizing  Fraud  and  Its  Ramifications  in  Affiliate  Marketing  Networks.'' %
                Journal of Cybersecurity (2016).

                \item Peter Snyder, Chris Kanich, and Michael K Reiter. %
                ``The Effect of Repeated Login Prompts on Phishing Susceptibility.'' %
                In Proceedings of the Workshop on Learning from Authoritative Security Experiment Results (LASER, 2016).

                \item Peter Snyder and Chris Kanich. %
                ``No Please,  After You:  Detecting Fraud in Affiliate Marketing Networks.'' %
                In Workshop on the Economics of Information Security (WEIS, 2015).

                \item Jason W Clark, Peter Snyder, Damon McCoy, and Chris Kanich. %
                ``I Saw Images I Didn't Even Know I Had: Understanding User Perceptions of Cloud Storage Privacy.'' %
                In Proceedings of the 33rd ACM Conference on Human Factors in Computing Systems (CHI, 2015).

                \item Peter Snyder. %
                ``Yao's Garbled Circuits: Recent Directions and Implementations.'' %
                In Written Critique and Presentation Exam (qualifier) Report (2014).

                \item Peter Snyder and Chris Kanich. %
                ``Cloudsweeper and Data-centric Security.'' %
                ACM SIGCAS Computers and Society (2014).

                \item Peter Snyder and Chris Kanich. %
                ``CloudSweeper:  Enabling Data-Centric Document Management for Secure Cloud Archives.'' %
                In Proceedings of the 2013 ACM Workshop on Cloud Computing Security (CCSW, 2013).
            \end{itemize}
    \end{description}
\end{singlespace}
